SSA based global code motion of identical computations

### 2017-04-17 paper.tex
code size

Code size remained almost the same as a result of code-motion as shown in Table~\cite{tab:code-size}.
Some bencmarks like 473.astar increased in code size by almost 2\%. This is because once the code-size
of a function decreases it becomes cheaper to inline. As we can see in Table-\cite{tab:stats}, four
more functions got inlined in 473.astar. Except for 447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk
all other benchmarks got more functions inlined.

>>>>

Code size remained almost the same as a result of code-motion as shown in Table~\cite{tab:code-size}.
The code size listed here is the text size (from linux size command) of the final executables for each benchmark.
Some bencmarks like 473.astar increased in code size by almost 2\%. This is because once the code-size
of a function decreases it becomes cheaper to inline. As we can see in Table-\cite{tab:stats}, four
more functions got inlined in 473.astar. Except for 447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk
all other benchmarks got more functions inlined.

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
  Benchmark       &   Baseline	        &  GCM & \%Incrase     \\\hline
  400.perlbench	  &   186,829,426	& 184,690,006	& 0.99 \\\hline
  401.bzip2	  &   76,337,033	& 75,942,641	& 0.99 \\\hline
  403.gcc         &   1,079,625,231	& 1,073,158,220	& 0.99 \\\hline
  429.mcf         &   78,336,298	& 77,859,513	& 0.99 \\\hline
  433.milc	  &   272,525,306	& 269,684,876	& 0.99 \\\hline
  444.namd	  &   78,354,313	& 77,875,603	& 0.99 \\\hline
  445.gobmk	  &   261,229,078	& 258,459,798	& 0.99 \\\hline
  447.dealII	  &   643,457,797	& 638,628,331	& 0.99 \\\hline
  450.soplex	  &   245,442,755	& 242,811,500	& 0.99 \\\hline
  453.povray	  &   499,034,715	& 494,785,035	& 0.99 \\\hline
  456.hmmer	  &   214,425,324	& 211,984,389	& 0.99 \\\hline
  458.sjeng	  &   89,612,524	& 88,803,166	& 0.99 \\\hline
  462.libquantum  &   84,762,158	& 84,077,905	& 0.99 \\\hline
  464.h264ref	  &   151,049,588	& 149,284,624	& 0.99 \\\hline
  470.lbm         &   71,878,726	& 71,775,405	& 1.00 \\\hline
  471.omnetpp	  &   382,661,268	& 379,123,833	& 0.99 \\\hline
  473.astar	  &   78,351,117	& 77,872,820	& 0.99 \\\hline
  482.sphinx3	  &   158,434,290	& 156,586,406	& 0.99 \\\hline
  483.xalancbmk	  &   22,485,708,759	& 22,455,060,569& 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Change in compilation time with and without code-motion on SPEC2006 at -Ofast}
  \label{tab:compile-time}
\end{table}

The compilation time actually reduced for most of the benchmarks as a result of code motion.
This is because as code-motion removes (congruent) instructions, the number of instructions
to be processed by later compilation passes also reduces. The compilation time listed here
is the total instruction count as outputted from valgrind (--tool=cachegrind).
